Detecting Facial Expressions in Professional Tennis Matches

### 2017-06-20 Report06-12.Rmd
moved folders

#csv files:
ALLmetaIMGnamed<-read_csv("ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")

>>>>

#csv files:
ALLmetaIMGnamed<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
SceneAttributes<-read_csv("../TableCSVs/SceneAttributes.csv")
FaceAttributes<-read_csv("../TableCSVs/FaceAttributes.csv")
SolutionSpecs<-read_csv("../TableCSVs/SolutionSpecifications.csv")
